\bf Service Chain Placement in SDNs \thanks{Research supported in part by Network Programming (Neptune) Consortium, Israel.}

### 2017-06-23 src/algorithm.tex
foo

In this section, 
assuming costs are integral and polynomial bounded in the input length,
we present an efficient algorithm to the \VPN{} problem.
We then argue that, using a standard scaling and rounding technique, we can use
the same computation to achieve a solution with a cost only
$1 + \varepsilon$ times greater that of the optimal solution, for any
$\varepsilon > 0$, i.e. an FPTAS also for an arbitrary cost function.
We also extend our algorithm when every physical arc carry some latency on it
and a global latency constraint is given.

We are given an instance of the \VPN{} problem 
\begin{align*}
D_v = (\beta , A_v)		\\
D_p = (v, A_p)		\\
(\sigma , \tau , s, t)	\\
(p_d, b_d, p_c, b_c, c)
\end{align*}
Also, for convenient and w.l.o.g, assume that $\sigma , \tau $ are dummy vertices, 
i.e. $c(\sigma , v) = c(\tau , v) = 0$ for every $v \in V_p$ and that
$b_d(\sigma\alpha) = b_d(\alpha\tau) = 0$ for every $\alpha \in V_v$.

We start by arguing that the minimum processing time required to embed some
$\alpha \gamma $-path into a vertex $v$ given a cost constraint can be computed
efficiently.
Let $P_{v}(\alpha , \gamma , C)$ denote the minimum processing required to embed
all the virtual vertices, excluding $\alpha $, on a $\alpha \gamma $-path into the physical
vertex $v$ with a cost constraint $C$.
$P$ can be computed recursively as follow:
\begin{align*}
&P_{v}(\alpha , \gamma , C) = 
\min_{\alpha \beta  \in A_v} P_{v}(\alpha , \beta , C - c(\gamma , v))
\\
&P(\alpha , \alpha , C) = 0
\\
&P(-, -, <0) = \infty
\end{align*}

We now show how to compute the optimal embedding.
Let $C(\gamma , w)$ denote the
optimal embedding of a $\sigma \gamma $-path into a $sw$-path.
Let $\pi:\beta  \to \N$ be any typological ordering of $\beta $. 
We claim that $C$ can be computed recursively as follow:
\begin{align*}
&C(\gamma , w) = 
\min_{\substack{
\alpha  : \pi(\alpha ) \leq \pi(\beta ), 
\\
vw \in A_p
}}
C(\alpha , u)
+
\argmin_{C : P_{w}(\beta , \gamma , C) \leq p_c(w)}
\\
&C(\sigma , w) = c(\sigma , w)
\end{align*}
Now, to compute the optimal embedding, one need to compute $C(\tau , t)$. 
We also note that in order to obey to the bandwidth constraints, 
one need to temporally remove all edges $\alpha \beta $ with bandwidth greater than
$b_c(v, w)$ from the virtual graph and only then compute $P_{w}(\beta , \gamma , C)$.
The above formulation is illustrated in Figure~\ref{fig:dp1}.

\begin{figure}[h]
\centering
\input{fig-dp2}
\caption[]{
\label{fig:dp1}
The optimal embedding of a $\sigma \gamma $-path into a $sv$ path can be
efficiently computed by breaking the problem into the problem of embedding 
a $\sigma \alpha $-path into a $su$-path (blue, dashed clouds) 
and the problem of embedding a $\beta \gamma $-path into $v$ (orange, dotted) 
where $b_d(\alpha , \beta) \leq b_c(u, v)$.
Virtual arcs with high bandwidth demand (dashed arc) need to be removed before
the computation of the optimal path embedding.
}
\end{figure}

>>>>

In this section, 
assuming costs are integral and polynomial bounded in the input length,
we present an efficient algorithm to the \VPN{} problem.
We then argue that, using a standard scaling and rounding technique, we can use
the same computation to achieve a solution with a cost only
$1 + \varepsilon$ times greater that of the optimal solution, for any
$\varepsilon > 0$, i.e. an FPTAS, for an arbitrary cost function.
We also extend our algorithm when every physical arc carry some latency on it
and a global latency constraint is given.
Our algorithms are recursive and can be efficiently computed using dynamic
programming.

We are given an instance of the \VPN{} problem 
\begin{align*}
\calG = (\calV, \calE)		\\
G = (V, E)		\\
(\sigma , \tau , s, t)	\\
(p, b, c)
\end{align*}

We start by arguing that a minimum cost 
$\alpha \gamma $-path with respect to vertex $v$ can be
found efficiently, that is a virtual $\alpha \gamma $-path that can be embedded 
into $v$ without violating its processing capacity that has the minimum cost
among all those paths.
Let $P_{v}(\alpha ,\gamma , C)$ 
denote the minimum processing required to embed all the virtual vertices, excluding $\alpha $, on a $\alpha \gamma $-path into the physical
vertex $v$ with a cost constraint $C$.
$P$ can be computed recursively as follow:
\begin{align*}
&P_{v}(\alpha , \gamma , C) = 
\min_{\alpha \beta  \in \calE} P_{v}(\alpha , \beta , C - c(\gamma , v))
\\
&P(\alpha , \alpha , C) = 0
\\
&P(-, -, <0) = \infty
\end{align*}
Computing $\min_{C : P_v(\alpha, \gamma, C) \leq p(v)}$ gives the desired
result.

We now show how to compute the optimal embedding.
Let $C(\gamma , w)$ denote the
optimal embedding of a $\sigma \gamma $-path into a $sw$-path.
Let $\pi:\beta  \to \N$ be any typological ordering of $\beta $. 
We claim that $C$ can be computed recursively as follow:
\begin{align*}
&C(\gamma , w) = 
\min_{\substack{
\alpha  : \pi(\alpha ) \leq \pi(\beta ), 
\\
vw \in E
}}
C(\alpha , u)
+
\argmin_{C : P_{w}(\beta , \gamma , C) \leq p_c(w)}
\\
&C(\sigma , w) = c(\sigma , w)
\end{align*}
Now, to compute the optimal embedding, one need to compute $C(\tau , t)$. 
We also note that in order to obey to the bandwidth constraints, 
one need to temporally remove all edges $\alpha \beta $ with bandwidth greater than
$b_c(v, w)$ from the virtual graph and only then compute $P_{w}(\beta , \gamma , C)$.
The above formulation is illustrated in Figure~\ref{fig:dp1}.

\begin{figure}[ht]
\centering
\input{fig-dp2}
\caption[]{
\label{fig:dp1}
The optimal embedding of a $\sigma \gamma $-path into a $sv$ path can be
efficiently computed by breaking the problem into the problem of embedding 
a $\sigma \alpha $-path into a $su$-path (blue, dashed clouds) 
and the problem of embedding a $\beta \gamma $-path into $v$ (orange, dotted) 
where $b_d(\alpha , \beta) \leq b_c(u, v)$.
Virtual arcs with high bandwidth demand (dashed arc) need to be removed before
the computation of the optimal path embedding.
}
\end{figure}

### 2017-06-23 src/graphs.tex
foo

In this section we consider the problem when the physical network is undirected.
Once again we seek to embed a virtual $\sigma\tau$-path 
into a simple physical $st$-path.
Note, that we still assume that the virtual graph is a DAG.

We extend our algorithm to work also for this case as well.
Recall that the problem on general graphs cannot be approximate at all,
thus we assume in this section that there exists an optimal embedding that uses
a physical path with at most $k$ \emph{heavy} vertices, thus are vertices with
degree greater than two (we do not assume anything about the physical network).
The modified algorithm includes a preprocessing stage that applies
random orientation to the physical network, it runs in time polynomial in the
input length and in $O(k!)$ and finds the optimal embedding with high probability.

The preprocessing stage is as follow:
let $V_h = {v_1, \ldots, v_h}$ be the set of heavy vertices, and let 
$\pi:[h] \to [h]$ be a random permutation.
Let $w_1, \ldots, w_l$ be a light path, that is, $w_1, w_l \in V_j$, 
$\forall 1 < i < l, w_i \notin V_h$, $\pi(w_1) < \pi(w_l)$, then
we direct the edges from $w_1$ to $w_l$ i.e. $(w_i, w_{i+1})$ for every $1 \leq
i \leq l - 1$.
One can verifies that this can be done efficiently and that when this process
terminates $G$ is a DAG, Figure~\ref{fig:orientation} depicts the preprocessing
stage.

\begin{figure}[h]
\input{fig-orientation}
\caption{
\label{fig:orientation}
The preprocessing stage: on the left is the undirected physical network,
Only the heavy nodes are drawn.
The numbers represent the permutation and the blue, dashed path represents a
path of an optimal embedding.
On the right side is the orientated physical network, 
note that it is enough that the internal ordering of the nodes on the blue,
dashed path is "correct" to ensure that the algorithm finds the optimal
embedding. }
\end{figure}

Completing the orientation, we use our previous algorithm to find an optimal
embedding.
We repeat this process, each time with a new independent random permutation, and
keep the best embedding so far.

We claim that with high probability, after $O(k!)$ iterations, the above
algorithm finds the optimal embedding, formally:

@@

\begin{proof}
Consider an optimal embedding and the order it induces on the heavy vertices,
If the random permutation order the heavy vertices in that order we are
guaranteed to find the optimal embedding.
This happens with probability $1/k!$ and the probability to miss the optimal
embedding after $xk!$ iterations is $1 - (1 - 1/k!)^{xk!} \leq 1 - e^{-x}$.
\end{proof}

>>>>

In this section we consider the problem when the physical network is undirected.
Once again we seek to embed a virtual $\sigma\tau$-path 
into a simple physical $st$-path.
Note, that we still assume that the virtual graph is a DAG. 
We extend our algorithm to work for this case as well.

Recall that the problem on general graphs cannot be approximate at all,
thus we assume in this section that there exists an optimal embedding that uses
a physical path with at most $k$ \emph{heavy} vertices, thus are vertices with
degree greater than two (we do not assume anything about the physical network).
The modified algorithm includes a preprocessing stage that applies
random orientation to the physical network, the entire algorithm runs in
$O(t(n)k!)$, where $t(n)$ is the time it takes to compute the optimal embedding when the
physical network is a DAG, and finds the optimal embedding with high
probability.

The preprocessing stage is as follow:
let $V_h$ be the set of heavy vertices, and let 
$\pi:V_h \to [|V_h|]$ be a random permutation.
For every \emph{light path} $w_1, \ldots, w_l$, that is, $w_1, w_l \in
V_h$, $\pi(w_1) < \pi(w_l)$, and $\forall_{1 < i < l}, w_i \notin V_h$,
we direct the edges from $w_1$ to $w_l$ i.e. $w_i \to w_{i+1}$ for every $1
\leq i \leq l - 1$.
One can verifies that this can be done efficiently and that when this process
terminates $G$ is a DAG, Figure~\ref{fig:orientation} depicts the preprocessing
stage.

\begin{figure}[ht]
\input{fig-orientation}
\caption{
\label{fig:orientation}
The preprocessing stage: on the left is the undirected physical network,
Only the heavy nodes are drawn.
The numbers represent the permutation and the blue, dashed path represents a
path of an optimal embedding.
On the right side is the orientated physical network, 
note that it is enough that the internal ordering of the nodes on the blue,
dashed path is "correct" to ensure that the algorithm finds the optimal
embedding. }
\end{figure}

Completing the orientation, we use our previous algorithm to find an optimal
embedding.
We repeat this process, each time with a new independent random permutation, and
keep the best embedding so far.
Note that if there is an optimal embedding using a physical path with at most
$k$ heavy vertices then it is sufficient that those vertices are ordered
"correctly" w.r.t $\pi$, regardless of the order $\pi$ applies to all other
heavy vertices, to ensure that the algorithm finds the optimal embedding.
We claim that with high probability, 
after $O(k!)$ iterations, the above algorithm finds the optimal embedding, formally:

@@

\begin{proof}
Consider an optimal embedding and the order it induces on the heavy vertices in
the physical path (at most $k$ such vertices), if the random permutation orders
the heavy vertices correctly, i.e. in that order, we are guaranteed to find the
optimal embedding.
This happens with probability $1/k!$ and the probability to miss the optimal
embedding after $xk!$ iterations is $1 - (1 - 1/k!)^{xk!} \leq 1 - e^{-x}$.
\end{proof}
